Master thesis

### 2017-06-14 05-Results.Rmd
Discussion draft 1

Most of functional traits had a significant long term influence on ecosystem outputs (figure \@ref(fig:ftVar)). On the other hand, few functional traits influenced final ecosystem structure. Only specific maximum diameter **dmax** add higher diversity for greater orders implying better eveness in species distributions. Regarding functional composition, traits fixed to mean did not change other functional traits density distribution. Moreover, seedrain did not seem to affect aboveground biomass and final ecosystem height and diameter structure. Seedrain constant fixed to 2 or 20 seed per hectare seemed to have a similar effect. Lower seedrain implied faster decrease of stem above 10 cm dbh and higher number of stem above 30 cm dbh after ecosystem resilience to disturbance (approximately 50 years). Lower seedrain than default decreased basal area over time. In addition, lower seedrain than default decreased equitability by increasing abundance of abundant species and decreasing abundance of less abundant species. See [Appendix 4: Sensitivity analysis] for further details.

>>>>

Most of functional traits had a significant long term influence on ecosystem outputs (figure \@ref(fig:ftVar)). On the other hand, few functional traits influenced final ecosystem structure. Only specific maximum diameter **dmax** add higher diversity for greater orders implying better eveness in species distributions. Regarding functional composition, traits fixed to mean did not change other functional traits density distribution. Moreover, seedrain did not seem to affect aboveground biomass and final ecosystem height and diameter structure. Seedrain constant fixed to 2 or 20 seed per hectare seemed to have a similar effect. Lower seedrain implied faster decrease of stem above 10 cm dbh and higher number of stem above 30 cm diameter at breast height after ecosystem resilience to disturbance (approximately 50 years). Lower seedrain than default decreased basal area over time. In addition, lower seedrain than default decreased equitability by increasing abundance of abundant species and decreasing abundance of less abundant species. See [Appendix 4: Sensitivity analysis] for further details.

### 2017-06-14 docs/master-thesis.tex
Discussion draft 1

Most of functional traits had a significant long term influence on
ecosystem outputs (figure \ref{fig:ftVar}). On the other hand, few
functional traits influenced final ecosystem structure. Only specific
maximum diameter \textbf{dmax} add higher diversity for greater orders
implying better eveness in species distributions. Regarding functional
composition, traits fixed to mean did not change other functional traits
density distribution. Moreover, seedrain did not seem to affect
aboveground biomass and final ecosystem height and diameter structure.
Seedrain constant fixed to 2 or 20 seed per hectare seemed to have a
similar effect. Lower seedrain implied faster decrease of stem above 10
cm dbh and higher number of stem above 30 cm dbh after ecosystem
resilience to disturbance (approximately 50 years). Lower seedrain than
default decreased basal area over time. In addition, lower seedrain than
default decreased equitability by increasing abundance of abundant
species and decreasing abundance of less abundant species. See
\protect\hyperlink{appendix-4-sensitivity-analysis}{Appendix 4:
Sensitivity analysis} for further details.

@@

>>>>

Most of functional traits had a significant long term influence on
ecosystem outputs (figure \ref{fig:ftVar}). On the other hand, few
functional traits influenced final ecosystem structure. Only specific
maximum diameter \textbf{dmax} add higher diversity for greater orders
implying better eveness in species distributions. Regarding functional
composition, traits fixed to mean did not change other functional traits
density distribution. Moreover, seedrain did not seem to affect
aboveground biomass and final ecosystem height and diameter structure.
Seedrain constant fixed to 2 or 20 seed per hectare seemed to have a
similar effect. Lower seedrain implied faster decrease of stem above 10
cm dbh and higher number of stem above 30 cm diameter at breast height
after ecosystem resilience to disturbance (approximately 50 years).
Lower seedrain than default decreased basal area over time. In addition,
lower seedrain than default decreased equitability by increasing
abundance of abundant species and decreasing abundance of less abundant
species. See
\protect\hyperlink{appendix-4-sensitivity-analysis}{Appendix 4:
Sensitivity analysis} for further details.

@@

\textbf{Take home messages:}

\subsection{\texorpdfstring{``Model
limits''}{Model limits}}\label{model-limits}

Discuss limits of the model with sensitivity analysis (insist in seed
rain constant importance).

\subsection{Diversity and tropical forest ecosystem
resilience}\label{diversity-and-tropical-forest-ecosystem-resilience}

\begin{itemize}
\tightlist
\item
  Diversity have a strong role in ecosystem resilience
\item
  Increasing functional diversity results in increased resilience
\item
  Species and functional richnesses is not directly increasing
  resilience
\item
  But increased species and functional richnesses will increase chance
  for high functional diversity
\item
  Functional dispersion decreased resilience when functional eveness
  increased resilience
\item
  Effectively high functional diversity needs eveness in order to better
  answer disturbance, if not the diversity is masked by ecosystem
  dominant species
\end{itemize}

\subsection{Biodiversity role in tropical forest ecosystem
resilience}\label{biodiversity-role-in-tropical-forest-ecosystem-resilience}

\begin{itemize}
\tightlist
\item
  Biodiversity net effect is almost always positive for ecosystems
  functions
\item
  Biodiversity effects answer to disturbance is split in two parts
\item
  First complementarity effects answer disturbance in first decades
  whereas the disturbance almost removed selection effect
\item
  Then complementarity effect will diminish toward extinction when
  selection effect is \emph{prendre le relais} to ensure biodiversity
  net effect
\item
  This patterns are even stronger for higher disturbances
\item
  In the case of selective logging the complementarity effect will thus
  be the only one playing between two \emph{rotations}
\item
  High forest diversity with important species complementarity through
  increased functional diversity is thus an advantage for forest
  restoration between two rotation in order to maintain both productive
  ecosystem and sustainable management
\end{itemize}

\subsection{Sylviculture ?}\label{sylviculture-2}

\subsection{Selective logging vs.~monoculture stand
?}\label{selective-logging-vs.monoculture-stand}

Results advocates for \textbf{sustainable} selective logging against
monoculture stand: high diversity will increase forest resilience and
thus improve logging \emph{turn-overs}. Even if monoculture stand are
\emph{irrégularisé} they will not reach mature forest diversity, and
consequently they will not reach its natural high resilience. But on the
other hand selective logging in tropical forest needs to be sustainable,
if not the diversity will slowly decrease after each turn-overs
degrading forest ecosystem functions, and resilience will become slower
and slower in a \emph{cercle vicieux}. Return toward
\citet{Zimmerman2012} discussion.
